`{peacesciencer}`:  A User’s  Guide  for  Quantitative  Peace Science in R

### 2021-06-10 user-guide/doc/ms.tex
add that little bit... little bits...

Finally, the creation and presentation of data in peace science should be 100\% transparent, which \texttt{\{peacesciencer\}} takes seriously in the following ways. The website for \texttt{\{peacesciencer\}} has several vignettes that describe its processes in some detail. These include how it provides reasonable estimates of democracy that may not be available in the Polity data or the Varieties of Democracy data and how a researcher can whittle dyadic dispute-years into true dyad-years through reasonable case exclusions. The project's Github contains a publicly available \texttt{data-raw} directory that shows how every data set included (and processed) in \texttt{\{peacesciencer\}} was created. The function manuals included \texttt{\{peacesciencer\}} contain ample documentation that clarifies what the function is doing, what it returns to the user, and why it is doing it this way. Users can also use the project's Github to point out bugs, ask for further clarification, and propose additions. \texttt{\{peacesciencer\}} takes seriously the Data Access and Research Transparency Initiative (DA-RT) initiative across all political science and endeavors for maximum transparency, leveraging open source and version control software to inform users of what data it uses and how it uses the data.

@@

This is not to say \texttt{\{peacesciencer\}} does everything, but \texttt{\{peacesciencer\}} can only evolve and expand on what it already does well. For example, \texttt{\{peacesciencer\}} does not right now handle \emph{k}-adic data (c.f. Poast 2010). However, the nature of \emph{k}-ads do not make for necessarily problematic data merges and should not be difficult to add for researchers who want it in future updates. Likewise, \texttt{\{peacesciencer\}} contains the Archigos leader data (Goemans, Gleditsch, and Chiozza 2009) and is able to transform that into interesting data at the dyad-level and state-level, but doing a leader-level analysis with information about leader willingness to use force (e.g. J. Carter and Smith 2020) is not right now available. However, these are possible expansions on what \texttt{\{peacesciencer\}} already does well. Thus, this package can only evolve to meet new analytical demands for the peace science community.

>>>>

Finally, the creation and presentation of data in peace science should be 100\% robust and transparent, which \texttt{\{peacesciencer\}} takes seriously in the following ways. The website for \texttt{\{peacesciencer\}} has several vignettes that describe its processes in some detail. These include how it provides reasonable estimates of democracy that may not be available in the Polity data or the Varieties of Democracy data and how a researcher can whittle dyadic dispute-years into true dyad-years through reasonable case exclusions. \texttt{\{peacesciencer\}} subjects itself to a battery of tests before publishing updates, making sure new features do not create duplicate entries in the original data (which is the surest sign of a botched merge). The project's Github contains a publicly available \texttt{data-raw} directory that shows how every data set included (and processed) in \texttt{\{peacesciencer\}} was created. The function manuals included \texttt{\{peacesciencer\}} contain ample documentation that clarifies what the function is doing, what it returns to the user, and why it is doing it this way. Users can also use the project's Github to point out bugs, ask for further clarification, and propose additions. \texttt{\{peacesciencer\}} takes seriously the Data Access and Research Transparency Initiative (DA-RT) initiative across all political science and endeavors for maximum transparency, leveraging open source and version control software to inform users of what data it uses and how it uses the data.

@@

This is not to say \texttt{\{peacesciencer\}} does everything, but \texttt{\{peacesciencer\}} can only evolve and expand on what it already does well. For example, \texttt{\{peacesciencer\}} does not right now handle \emph{k}-adic data (c.f. Poast 2010). However, the nature of \emph{k}-ads do not make for necessarily problematic data merges and should not be difficult to add for researchers who want it in future updates. Likewise, \texttt{\{peacesciencer\}} contains the Archigos leader data (Goemans, Gleditsch, and Chiozza 2009) and is able to transform that into interesting data at the dyad-level and state-level, but doing a leader-level analysis with information about leader willingness to use force (e.g. J. Carter and Smith 2020) is not right now available. However, these are possible expansions on what \texttt{\{peacesciencer\}} already does well. Thus, this package can only evolve to meet new analytical demands for the peace science community. Users are free to request new features as ``issues'' on the project's Github.

### 2021-06-10 user-guide/ms.Rmd
add that little bit... little bits...

Finally, the creation and presentation of data in peace science should be 100% transparent, which `{peacesciencer}` takes seriously in the following ways. The website for `{peacesciencer}` has several vignettes that describe its processes in some detail. These include how it provides reasonable estimates of democracy that may not be available in the Polity data or the Varieties of Democracy data and how a researcher can whittle dyadic dispute-years into true dyad-years through reasonable case exclusions. The project's Github contains a publicly available `data-raw` directory that shows how every data set included (and processed) in `{peacesciencer}` was created. The function manuals included `{peacesciencer}` contain ample documentation that clarifies what the function is doing, what it returns to the user, and why it is doing it this way. Users can also use the project's Github to point out bugs, ask for further clarification, and propose additions. `{peacesciencer}` takes seriously the Data Access and Research Transparency Initiative (DA-RT) initiative across all political science and endeavors for maximum transparency, leveraging open source and version control software to inform users of what data it uses and how it uses the data.

@@

This is not to say `{peacesciencer}` does everything, but `{peacesciencer}` can only evolve and expand on what it already does well. For example, `{peacesciencer}` does not right now handle *k*-adic data [c.f. @poast2010mdd]. However, the nature of *k*-ads do not make for necessarily problematic data merges and should not be difficult to add for researchers who want it in future updates. Likewise, `{peacesciencer}` contains the Archigos leader data [@goemansetal2009ia] and is able to transform that into interesting data at the dyad-level and state-level, but doing a leader-level analysis with information about leader willingness to use force [e.g. @cartersmith2020fml] is not right now available. However, these are possible expansions on what `{peacesciencer}` already does well. Thus, this package can only evolve to meet new analytical demands for the peace science community.

>>>>

Finally, the creation and presentation of data in peace science should be 100% robust and transparent, which `{peacesciencer}` takes seriously in the following ways. The website for `{peacesciencer}` has several vignettes that describe its processes in some detail. These include how it provides reasonable estimates of democracy that may not be available in the Polity data or the Varieties of Democracy data and how a researcher can whittle dyadic dispute-years into true dyad-years through reasonable case exclusions. `{peacesciencer}` subjects itself to a battery of tests before publishing updates, making sure new features do not create duplicate entries in the original data (which is the surest sign of a botched merge).  The project's Github contains a publicly available `data-raw` directory that shows how every data set included (and processed) in `{peacesciencer}` was created. The function manuals included `{peacesciencer}` contain ample documentation that clarifies what the function is doing, what it returns to the user, and why it is doing it this way. Users can also use the project's Github to point out bugs, ask for further clarification, and propose additions. `{peacesciencer}` takes seriously the Data Access and Research Transparency Initiative (DA-RT) initiative across all political science and endeavors for maximum transparency, leveraging open source and version control software to inform users of what data it uses and how it uses the data.

@@

This is not to say `{peacesciencer}` does everything, but `{peacesciencer}` can only evolve and expand on what it already does well. For example, `{peacesciencer}` does not right now handle *k*-adic data [c.f. @poast2010mdd]. However, the nature of *k*-ads do not make for necessarily problematic data merges and should not be difficult to add for researchers who want it in future updates. Likewise, `{peacesciencer}` contains the Archigos leader data [@goemansetal2009ia] and is able to transform that into interesting data at the dyad-level and state-level, but doing a leader-level analysis with information about leader willingness to use force [e.g. @cartersmith2020fml] is not right now available. However, these are possible expansions on what `{peacesciencer}` already does well. Thus, this package can only evolve to meet new analytical demands for the peace science community. Users are free to request new features as "issues" on the project's Github.
